SDR enhancement by clouds

### 2024-03-27 article/article.Rmd
Commit 2024-03-27 12:12

The shortwave solar irradiance, reaches the Earth's surface, is the main energy
source of the planet. It drives and governs the climate.
It has direct practical application, in different energy production method.
.... cite ....
The variability of its intensity, can cause difficulties in predicting the yield and
designing the appropriate equipment.
.... cite ....
An aspect of this variability are the interaction with the clouds, where locally, under some
conditions the total shortwave irradiance reaching the ground can be higher than the
expected clear sky irradiance.
.... cite ....
Those enhancements have been reported to be able to exceed .... and duration.
.... cite ....

The underling mechanism of those events have been studied, with the main factor to be
.... cite ...
The forward scattering of clouds near the sun has been observed to produce cases of
extreme enhancement irradiances [@Yordanov2015].

Gueymard, 2017; Veerman et al., 2022)
Methods of identification in the literature include the use of a clear sky radiation
modelel

>>>>

The shortwave solar irradiance, reaches the Earth's surface, is the main energy
source of the planet. It drives and governs the climate.
It has direct practical application, in different energy production method.
.... cite ....
The variability of its intensity, can cause difficulties in predicting the yield and
designing the appropriate equipment.
.... cite ....
A big aspect of this variability are the interaction with the clouds. In general
clouds, absorb part of the solar irradiance, but under certain conditions, can
enhance the total shortwave irradiance reaching the ground. This effect can locally
increase the observed total shortwave irradiance higher than the expected clear sky
irradiance [see references therein].
.... cite ....
Those enhancements have been reported to be able to exceed .... and duration.
.... cite ....
@Martins2022

Some of the proposed underling mechanisms of those events have been summarized
by @Gueymard2017, and include scattering on the edge of cumulus clouds or through
thin cirrus.  Further investigation with radiation transfer modeling methods and
observations have pointed as the prevailing mechanism, the forward Mie scattering
[@Pecenak2016; @Thuillier2013; @Yordanov2013; @Yordanov2015], through the clouds.
The overall phenomenon depends on different interactive factors, that include cloud
thickness and constitution, and the relative position of the sun, the clouds, and the
observer.  As such, there multiple contributing mechanism can  create the
observed irradiance enhancements.

The forward scattering of clouds near the sun has been observed to produce cases of
extreme enhancement irradiances [@Yordanov2015].

It has been reported than enhancements events can interfere in the comparison of
ground data and satellite observe ovations [@Damiani2018]

Instruments respose ....
@Martins2022

Study of the mechanism has also been done with modeling of different cloud types and
atmospheric conditions.
@Gueymard2017; @Veerman2022

Methods of identification in the literature usually include the use of a simulated clear sky radiation
@Vamvakas2020; @Mol2023;
